\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Mike Zeng} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(408) 430-7654 \\ Iowa City, IA} \address{\href{mailto:mzeng1417@gmail.com}{mzeng1417@gmail.com} \\  \href{https://www.linkedin.com/in/mike-zeng-189756257/} {www.linkedin.com/in/mike-zeng-189756257}   
\\ \href{https://mzen.dev}{mzen.dev}} 
\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------
%
%\begin{rSection}{OBJECTIVE}

%{Dual-enrolled student at high school and college seeking internship and entry-%level software engineering roles to gain experience in the industry. Planning %to pursue a bachelor's degree in Computer Science in the future.}


%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf University of Iowa -} Iowa City, IA  \hfill {Expected May 2027}\\ 
Relevant Coursework: Data Structures, Algorithms, Operating Systems, Computer Networks, Software Engineering, Theory of Computation, Distributed Systems
%%{\bf Bachelor of Computer Science}, Stanford University \hfill {2014 - 2017}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

%
\begin{rSection}{Experiences}
\textbf{University of Iowa Hydroinformatics Lab} \hfill Oct 2024-Present\\
Research Assistant \hfill \textit{Iowa City, IA}
 \begin{itemize}
  \itemsep -3pt {} 
  \item Proposed a system for reducing onsite visit costs with a web platform using visualization of harmful algae blooms through satellite data.
  \item Used Javascript to implement a filter for 2000+ pieces of satellite data using Google Earth Engine API and a mathematical formula on images to achieve 100\% accuracy of prediction.
  \item Wrote tests to ensure that UI features work as intended.
  \end{itemize}
 %/
%\textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
%Company Name \hfill \textit{San Francisco, CA}
 %\begin{itemize}
   % \itemsep -3pt {} 
     %\item Achieved X\% growth for XYZ using A, B, and C skills.
    % \item Led XYZ which led to X\% of improvement in ABC
   % \item Developed XYZ that did A, B, and C using X, Y, and Z. 
% \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Shards of the Grid} 
\begin{itemize}
   \itemsep -3pt {} 
     \item Collaborated with a team of 5 students to build a SaaS web game on Heroku to get positive reviews from University of Iowa faculty.
     \item Developed Figma mockups \& public wiki, holding weekly customer meetings with clients for acceptance tests \&
     development feedback. Participated in daily scrum meetings \& pair programming sessions to complete
     100\% of user stories by project deadlines.
     \item Wrote cucumber feature tests for Ruby on Rails views testing as well as RSpec tests for models and controllers,
     ensuring 99\% code coverage. Managed Github workflows for CI/CD setup \& issue/PR templates.
\end{itemize}


%25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}

\item \textbf{Page Processor} 
\begin{itemize}
   \itemsep -3pt {} 
     \item Developed a page-based word processor for creating and managing any document that severely relies on paging
     using FastAPI, Postgres, HTML, and JavaScript.
\end{itemize}

\item \textbf{Proxmox Virtual Homelab} 


\begin{itemize}
   \itemsep -3pt {} 
     \item Engineered a dense virtualization environment running NAS, DNS/DHCP, Postgres, NGINX, Kubernates, re-
     mote workstations, OpenVPN, Red Hat Enterprise Linux.
\end{itemize}

%\item \textbf{A Chance to Light This World.} {Build a 2D game that does something and had quantified success using Unity, Clip Studio Paint, and C. This project's description spans two lines and also won an award.}
\end{rSection} 
%----------------------------------------------------------------------------------------
\begin{rSection}{Awards} 
  \vspace{-1.25em}
  \item \textbf{United States of America Coding Olympiad (USACO)} 
  \begin{itemize}
     \itemsep -3pt {} 
       \item Qualified to participate in Silver Division, top 25\% of 12,000 participants across the United States for data
       structures, algorithms, and C++.
  \end{itemize}

  \item \textbf{Technology Student Association Tests of Engineering, Aptitude, and Math (TEAMS)} 
  \begin{itemize}
     \itemsep -3pt {} 
       \item Placed 1st in Iowa for a test on physics/computer science and the engineering build contest.
       
  \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Skills} 
\textbf{Languages:} Java, C/C++, C\#, Python, JavaScript/TypeScript, Rust, HTML/CSS, Ruby, SQ, SAS \\
\textbf{Frameworks:} Svelte, React, Django, Rails, FastAPI, TailwindCSS/Bootstrap, TensorFlow, PyTorch\\
\textbf{Technologies:} AWS, GCP, Postgres, MySQL, Git, Linux, NGINX, Unreal Engine, Unity

%\begin{itemize}
    %\item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
%\end{itemize}
\end{rSection}


\end{document}
